---
title: "Lab 9"
author: "Jack Brown"
format: html
editor: visual
---

## Lab 9 - Generative Art

```{r}
library(ggplot2)
library(tibble)
library(dplyr)
```

## Part 1

```{r}
sample_canva <- function(seed = NULL) {
  if(!is.null(seed)) set.seed(seed)
  sample(ggthemes::canva_palettes, 1)[[1]]
}
```

```{r}
sample_data <- function(seed = NULL, n = 100){
  if(!is.null(seed)) set.seed(seed)
  dat <- tibble(
    x0 = runif(n),
    y0 = runif(n),
    x1 = x0 + runif(n, min = -.2, max = .2),
    y1 = y0 + runif(n, min = -.2, max = .2),
    shade = runif(n), 
    size = runif(n),
    shape = factor(sample(0:22, size = n, replace = TRUE))
  )
}
```

```{r}
polar_styled_plot <- function(data = NULL, palette) {
  ggplot(
    data = data,
    mapping = aes(
      x = x0,
      y = y0,
      xend = x1,
      yend = y1,
      colour = shade,
      size = size
    )) + 
    coord_polar(clip = "off") +
    scale_y_continuous(
      expand = c(0, 0),
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) +
    scale_x_continuous(
      expand = c(0, 0), 
      limits = c(0, 1), 
      oob = scales::oob_keep
    ) + 
    scale_colour_gradientn(colours = palette) + 
    scale_size(range = c(0, 10)) + 
    theme_void() + 
    guides(
      colour = guide_none(),
      size = guide_none(),
      fill = guide_none(),
      shape = guide_none()
    )
}
```

```{r}
dat1 <- sample_data(n = 500, seed = 123) |>
  mutate(y1 = y0, size = size / 2)

dat2 <- sample_data(n = 350, seed = 35) |>  
  mutate(y0 = .3 + y0 * .6, y1 = .3)

dat3 <- as.data.frame(list(x1=0,y1=0))

polar_styled_plot(palette = c("cyan", "white", "gold")) + 
  geom_segment(data = dat1) + 
  geom_segment(data = dat1 |> mutate(y1 = y1 - .2, y0 = y0 - .2)) +
  geom_segment(data = dat1 |> mutate(y1 = y1 - .4, y0 = y0 - .4)) + 
  geom_segment(
    data = dat2 |> mutate(size = size / 10), 
    lineend = "round", 
    colour = "green3"
  ) +
  geom_segment(
    data = dat2 |> mutate(size = size / 40), 
    lineend = "round", 
    colour = "green4"
  )  + geom_point(data=dat3, aes(x1,y1), size = 32, col="brown")
```

**360 Bird's Eye View of a Palm Tree on the Beach**

## Part 2

```{r}
library(rayshader)
library(tibble)
library(ambient)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(tictoc)
library(dplyr)
```

```{r}
is_within_circle <- function(x_coord, y_coord, x_center, y_center, radius) {
  (x_coord - x_center)^2 + (y_coord - y_center)^2 < radius^2
}
```

```{r}
additive_circles <- function(n = 5, pixels = 1000, seed = NULL) {
  
  if(!is.null(seed)) set.seed(seed)
  
  # setup canvas
  art <- long_grid(
    x = seq(0, 1, length.out = pixels),
    y = seq(0, 1, length.out = pixels)
  )
  art$paint <- 50
  
  for(i in 1:n) {
    
    # sample a random circle
    x_center <- runif(1, min = .1, max = .9)
    y_center <- runif(1, min = .1, max = .9)
    radius <- runif(1, min = .005, max = .05)
    
    # add +1 to all points inside the circle
    art <- art |>
      mutate(
        paint = paint + is_within_circle(
          x, y, x_center, y_center, radius
        )
      )
  }
  
  # normalise paint to [0, 1] range and return
  art$paint <- normalise(art$paint)
  return(art)
}
```

```{r}
circle_art <- additive_circles(1500, seed = 2)

circle_array <- circle_art |>
  as.array(value = paint) 

circle_array |> 
  image(axes = FALSE, asp = 1, useRaster = TRUE, col=c("cyan2", "green4", "brown"))
```

***The Hidden Lands of the Flat Earth***: A completely random and baseless rendering that mimics the completely random and baseless belief that some hold that the Earth is flat. Believers of a Flat Earth have shared images very similar to this one, which supposedly is a map of the "real" Earth, displaying has "Hidden Lands", which are tons of different groups of continents, separated by ice walls. \[<https://www.reddit.com/r/MapPorn/comments/cc5sfm/flat_earth_hidden_lands_map_which_shows_what_the/>\]

\[<https://www.reddit.com/r/FacebookScience/comments/15xz270/the_true_map_of_the_earth_beyond_the_ice_wall/>\]

This art is made by rendering lots of circles, and coloring the positive, negative, and overlapping space. On a 1x1 plot, I allowed the radius of the circles to range from between 0.005 and 0.05, and allowed the (x,y) coordinates of centers of each circle range from anywhere from 0.1 to 0.9
